A New Method of Modelling Tuneable Lasers with Functional Composition

### 2020-01-19 Papers/Journal/Tuneable_Lasers.tex
Inverted colour scheme

\section{Introduction}
\label{sec:intro}
A tuneable laser has the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}. Tuneable lasers simultaneously lase at all frequencies within this bandwidth. This tuneability leads to applications in spectroscopy and high resolution imaging, such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}. A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.

@@

To compute $\mathcal{F}(A)$, given the initial pulse \eqref{eq:A0}, we iteratively compute the effect of each process map from \eqref{eq:effects}. Now, by equating $\mathcal{F}(A)$ and $A \textrm{e}^{i \phi}$ we obtain a system of equations. In particular, 
\begin{align}
	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
	C = .
	\label{eq:chirp}
\end{align}

>>>>

\section{Introduction}
\label{sec:intro}
A tuneable laser has the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}. Tuneable lasers simultaneously lase at all frequencies within this bandwidth. This tuneability leads to applications in spectroscopy and high resolution imaging, such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultrafast processes \cite{silfvast}. A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.

@@

To compute $\mathcal{F}(A)$, given the initial pulse \eqref{eq:A0}, we iteratively compute the effect of each process map from \eqref{eq:effects}. Now, by equating $\mathcal{F}(A)$ and $A \textrm{e}^{i \phi}$ we obtain a system of equations. In particular,
\begin{gather}
	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
	C = \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
	\label{eq:chirp}
\end{gather}
